The Eclipse Integrated Computational Environment

### 2017-05-30 src/main.tex
Fixed keywords. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Pushing changes from Sam's edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage[hyphens]{url}

@@

Problems in modeling and simulation require significantly different
workflow management technologies than standard grid-based workflow
management systems. Computational scientists typically interact with
simulation software in a feedback driven way where solutions and
workflows are developed iteratively and simultaneously. This work
describes common activities in workflows and how combinations of these
activities form unique workflows. It presents the Eclipse Integrated
Computational Environment as a workflow management system and
development environment for the modeling and simulation community.
Examples of the Environment's applicability to problems in energy
science, general multiphysics simulations, quantum computing and other
areas are presented as well as its impact on the community.

@@

\begin{keyword}
\sep
\sep 
supercomputing

>>>>

\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{float}
\usepackage[hyphens]{url}

@@

Problems in modeling and simulation require significantly different
workflow management technologies than standard grid-based workflow
management systems. Computational scientists typically interact with
simulation software in a feedback-driven way where solutions and
workflows are developed iteratively and simultaneously. This work
describes common activities in workflows and how combinations of these
activities form unique workflows. It presents the Eclipse Integrated
Computational Environment as a workflow management system and
development environment for the modeling and simulation community.
Examples of the Environment's applicability to problems in energy
science, general multiphysics simulations, quantum computing, and other
areas are presented along with its impact on the community at large.

@@

\begin{keyword}
workflows
\sep 
workflow management
\sep
supercomputing
\sep
usability
\sep
eclipse
